Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-10-28 tex/scam/introduction.tex
new citation

Recently, there has been increased research activity on shape-constrained estimation. \cite{guntusen:13} analyze univariate convex regression and show surprisingly that the risk of the MLE is adaptive to the complexity of the true function. \cite{seijo2011nonparametric} and \cite{Lim:12} study maximum likelihood estimation of multivariate convex regression and independently establish its consistency. \cite{Cule:10} and \cite{kim2014global} analyze log-concave density estimation and prove consistency of the MLE; the latter further show that log-concave density estimation has minimax risk lower bounded by $n^{-2/(d+1)}$ for $d \geq 2$, refuting a common notion that the condition of convexity is equivalent, in estimation difficulty, to the condition of having two bounded derivatives. \cite{pya2014shape} and then \cite{chen2014generalised} both look at additive shape-constrained models. To the best of our knowledge though, there has not yet been any work on variable selection and high-dimensional estimation of convex functions.

@@

Perhaps more closely related to the present work is the framework
studied by \cite{Raskutti:12} for sparse additive models, where sparse
regression is considered under an additive assumption, with each
component function belonging to an RKHS.  An advantage of working over
an RKHS is that nonparametric regression with a sparsity-inducing
regularization penalty can be formulated as a finite dimensional
convex cone optimization.  On the other hand, smoothing parameters for
the component Hilbert spaces must be chosen, leading to extra tuning
parameters that are difficult to select in practice.  In addition, the
additive model must be assumed to be correct for consistent variable
selection.

>>>>

Recently, there has been increased research activity on shape-constrained estimation. \cite{guntusen:13} analyze univariate convex regression and show surprisingly that the risk of the MLE is adaptive to the complexity of the true function. \cite{seijo2011nonparametric} and \cite{Lim:12} study maximum likelihood estimation of multivariate convex regression and independently establish its consistency. \cite{Cule:10} and \cite{kim2014global} analyze log-concave density estimation and prove consistency of the MLE; the latter further show that log-concave density estimation has minimax risk lower bounded by $n^{-2/(d+1)}$ for $d \geq 2$, refuting a common notion that the condition of convexity is equivalent, in estimation difficulty, to the condition of having two bounded derivatives. Additive shape-constrained estimation has also been studied; \cite{pya2014shape} propose a penalized B-spline estimator while \cite{chen2014generalised} show the consistency of the MLE. To the best of our knowledge however, there has been no work on variable selection and high-dimensional estimation of convex functions.

@@

Perhaps more closely related to the present work is the framework
studied by \cite{Raskutti:12} for sparse additive models, where sparse
regression is considered under an additive assumption, with each
component function belonging to an RKHS.  An advantage of working over
an RKHS is that nonparametric regression with a sparsity-inducing
regularization penalty can be formulated as a finite dimensional
convex cone optimization.  On the other hand, smoothing parameters for
the component Hilbert spaces must be chosen, leading to extra tuning
parameters that are difficult to select in practice. \cite{huang2010variable} 
too formulate sparse additive spline fitting as a convex optimization but
their procedure too requires a smoothing parameter in the form of 
a truncation level for the spline basis.
